Improving \textsl{Gaia} parallax precision \\ with a data-driven model of stars

### 2017-06-06 paper/paper.tex
Added full affiliations

\author[0000-0002-3962-9274]{Boris Leistedt}
\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, room 1005, New York, NY 10003, USA}

@@

This project was partially supported by This research was partially supported by
  the \acronym{NSF} (\acronym{AST-1517237}),
  \acronym{NASA} (grant \acronym{NNX12AI50G}),
  and the Moore-Sloan Data Science Environment at \acronym{NYU}.
It made use of the \acronym{NASA} Astrophysics Data System.
All the code used in this project is available online\footnote{\url{https://github.com/andersdot/photoParallax}} under an open-source license.

>>>>

\author[0000-0002-3962-9274]{Boris Leistedt}
\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, room 1005, New York, NY 10003, USA}
\affil{NASA Einstein Fellow}

@@

This research was partially supported by
  the \acronym{NSF} (\acronym{AST-1517237}),
  \acronym{NASA} (grant \acronym{NNX12AI50G}),
  and the Moore-Sloan Data Science Environment at \acronym{NYU}. 
  BL was supported by the National Aeronautics and Space Administration through Einstein Postdoctoral Fellowship Award Number PF6-170154.
It made use of the \acronym{NASA} Astrophysics Data System.
All the code used in this project is available online\footnote{\url{https://github.com/andersdot/photoParallax}} under an open-source license.
